\chapter{The Heist at Titan Station}

Titan Station orbited Saturn's largest moon like a glittering jewel, its three rotating rings providing artificial gravity for the fifty thousand souls who called it home. It was the crown jewel of the outer system colonies, a hub of commerce, industry, and most importantly for Captain Zara Vega's purposes, the location of the Titan Mercantile Bank's primary vault.

``Tell me again why this isn't suicide,'' Jax said, studying the holographic projection of the station floating above the \textit{Crimson Revenge}'s planning table.

``Because we're not going to rob the bank,'' Zara replied, manipulating the projection to highlight a different section. ``We're going to rob the people robbing the bank.''

The briefing room fell silent as her senior crew digested this information. After a moment, Kira raised her hand.

``Captain, I think you're going to need to explain that one.''

Zara smiled. ``Six weeks ago, our friend Diana Marsh reached out with some interesting intelligence. It seems the Titan Mercantile Bank has been cooking its books, hiding massive losses from bad investments in failed colony ventures. They're technically insolvent.''

``So?'' Chen asked. ``Banks fail all the time. The government bails them out, executives get golden parachutes, and everyone else gets screwed. Same old story.''

``Not this time,'' Zara continued. ``The bank's board of directors has a different plan. They're going to stage a robbery---blame it on pirates, collect the insurance, and disappear with the real treasure before anyone realizes the vault was already empty.''

Understanding dawned on Malik's face. ``They're going to frame us. Pirates hit the bank, authorities crack down on everyone, and the executives walk away clean.''

``Exactly. Which is why we're going to beat them to it.'' Zara expanded the projection, showing the station's docking rings. ``In four days, during the Titan Day celebrations when security is focused on crowd control, a team of 'pirates' hired by the bank will hit the vault. They'll make a big show of it, lots of explosions and threats, while the executives quietly transfer the real assets off-station.''

``And we intercept those transfers,'' Jax said, beginning to see the plan.

``Better. We replace their hired pirates.'' Zara's smile turned predatory. ``They're expecting a crew of thugs to show up, cause chaos, and take the fall. Instead, they get us. We play along, let them think their plan is working, then take everything---the insurance scam loot and whatever else we can grab on the way out.''

``That's...'' Kira paused, searching for words. ``That's either brilliant or insane.''

``Little of both,'' Zara admitted. ``But think about it. We're not stealing from hardworking colonists. We're stealing from thieves who are trying to steal from everyone else. It's almost righteous.''

``Almost,'' Malik muttered, but he was smiling.

The next three days were spent in meticulous preparation. The \textit{Crimson Revenge} docked at a maintenance station two jumps away from Titan, officially undergoing repairs while Zara's crew made their actual preparations. False identities were crafted, equipment was sourced, and most importantly, contact was made with the bank's inside man.

Gerald Hoffman was everything Zara expected from a corrupt bank executive---soft, nervous, and utterly convinced of his own cleverness. They met in a seedy bar on the maintenance station, Zara playing the role of a pirate captain eager for an easy score.

``You understand the plan?'' Hoffman asked for the third time, sweating despite the bar's cool temperature. ``You hit the vault during the height of the celebrations. Make it loud, make it messy. Security will respond, you take some prop money we've prepared, maybe rough up a few guards for show. Then you run.''

``And our payment?'' Zara asked, pitching her voice lower, rougher.

``Half now, half when the job's done.'' Hoffman slid a credit chip across the table. ``Fifty thousand credits. More than you'd make in a year of regular piracy.''

Zara palmed the chip, noting the bank routing codes embedded in its encryption. Another piece of evidence for later. ``And the vault codes?''

``You won't need them. The vault will be... malfunctioning at the specified time. Security glitch, happens sometimes with these old systems.'' Hoffman's smile was oily. ``Just walk right in.''

``Convenient.''

``That's what you're being paid for. Convenience.'' Hoffman stood to leave, then paused. ``One more thing. There might be some collateral damage. Guards who don't know they're supposed to let you go. That won't be a problem, will it?''

``We're pirates,'' Zara said flatly. ``What do you think?''

Hoffman's smile widened. ``Perfect. I knew we picked the right crew.''

After he left, Jax emerged from the shadows where he'd been recording the entire conversation. ``Got it all. Audio, video, biometric confirmation. If we needed to prove the bank was behind this...''

``We won't,'' Zara said. ``We're not in the justice business. We're in the taking-what-we-can-get business. But it's nice to have insurance.''

Titan Day arrived with all the pageantry fifty thousand homesick humans could muster. The station's promenades were packed with revelers celebrating the anniversary of Titan Colony's founding. Security was indeed focused on crowd control, leaving other areas of the station notably understaffed.

Zara's team moved through the maintenance tunnels like ghosts. Eight of her best---Jax, Kira, Chen, and five others chosen for their specific skills. They wore the garish outfits Hoffman had provided, looking like stereotypical pirates from a bad holo-drama.

``I feel ridiculous,'' Kira muttered, adjusting the bandolier of fake plasma charges across her chest.

``That's the point,'' Zara replied. ``We're not supposed to look professional. We're supposed to look like the kind of idiots who would take this job.''

They reached the service entrance to the bank right on schedule. As promised, the security systems were offline, doors opening at their approach. Too easy, but that was the point. This was supposed to be theater.

The main vault was a massive circular chamber in the heart of the bank, its walls lined with safety deposit boxes and secured storage units. At its center sat the primary cash reserve---or what was supposed to be the cash reserve. Even from across the room, Zara could tell the credit containers were props, their security seals obviously fake to a trained eye.

``Positions,'' she ordered. ``Make it look good for the cameras.''

Her crew spread out, attaching fake charges to walls, waving weapons at non-existent threats. The few guards they encountered were clearly in on it, falling down at the slightest contact, their weapons firing harmlessly into walls.

``Vault secure!'' Jax announced loudly, playing to the security recordings. ``Loading the goods!''

That's when Zara noticed the terminal in the corner, still active despite the supposed security shutdown. She moved closer, recognizing the executive access interface. Hoffman or one of his conspirators must have used it recently.

A few quick commands and she was in, her years of forced education under Morrison finally paying off. The terminal showed recent transfers, massive amounts being moved to off-station accounts. But there was something else---a secondary transfer scheduled for thirty minutes from now, after the ``robbers'' were supposed to have fled.

``Interesting,'' she murmured, quickly downloading the data to her personal storage.

``Captain,'' Chen's voice crackled over the comm. ``We've got movement. Security's responding faster than expected.''

``Already?'' Zara checked her chronometer. They were ahead of schedule. ``How many?''

``Two squads, moving with purpose. I don't think these guys got the memo about letting us go.''

A cold realization washed over Zara. Of course. Hoffman needed the pirates to take the fall, but he also needed them dead. No loose ends. The security forces converging on their position weren't in on the scam---they were doing their jobs, responding to a real bank robbery.

``Change of plans,'' Zara announced. ``This isn't theater anymore. Hoffman set us up to die here. Kira, Chen, get to the executive level. Find Hoffman before he rabbits. Everyone else, we're leaving. Now.''

``But the fake money---'' someone started.

``Forget it. We've got bigger fish to fry.'' Zara's fingers flew over the terminal, initiating the transfer she'd discovered but changing the destination to one of her own shell accounts. ``There. Now let's move.''

They burst out of the vault just as security arrived. These weren't the play-acting guards from before---these were real station security, armed and trained. Plasma fire filled the corridor as both sides took cover.

``Suppress and move!'' Zara ordered, laying down covering fire. ``We push through to the service tunnels!''

The running battle that followed was chaos incarnate. Zara's crew fought with desperate efficiency, using every trick and tactic learned in years of piracy. Security fought with determination, believing they were protecting their home from raiders.

``Captain!'' Kira's voice over comms. ``We've got Hoffman! He was trying to access an executive escape pod!''

``Bring him. We might need a hostage.''

They rendezvoused at a maintenance junction, Hoffman being dragged along by Chen, the executive's face pale with terror.

``You weren't supposed to survive!'' he squealed. ``The plan was perfect!''

``Your plan was amateur hour,'' Zara snarled. ``Did you really think you could use pirates as pawns and walk away clean?''

More security forces were converging on their position. The route to their ship was cut off, and station alarms were wailing. In minutes, the entire security apparatus of Titan Station would be mobilized against them.

``There,'' Jax pointed to a maintenance schematic on the wall. ``Cargo transport tubes. They lead to the outer docking ring.''

``Those aren't meant for people,'' Malik protested.

``Neither is spacing, but that's where we're headed if we don't move.'' Zara made the decision. ``Into the tubes. Move!''

The next few minutes were a nightmare of claustrophobic crawling through tubes meant for cargo containers, the sound of security forces trying to cut through behind them. Hoffman whimpered constantly until Jax threatened to leave him behind.

They emerged in a cargo processing area near the outer docks, alarms still blaring throughout the station. The \textit{Crimson Revenge} was berthed three sections away, but might as well have been on the other side of the system for all the good it did them.

``Now what?'' Kira asked, checking her weapon's charge.

Zara looked around, her mind racing. They needed a distraction, something big enough to draw security away. Her eyes fell on Hoffman, then on the cargo containers being loaded onto a massive freight hauler.

``Hoffman,'' she said sweetly. ``You're going to make an announcement.''

``What? No, I can't---''

Zara's pistol pressed against his temple changed his mind.

Five minutes later, Hoffman's voice echoed through the station's communication system. Under Zara's direction, he confessed everything---the bank's insolvency, the insurance fraud, the plan to frame pirates and disappear with the remaining assets. He named names, provided account numbers, and revealed where the real money had gone.

The effect was immediate. The ordered response to the bank robbery dissolved into chaos as security forces tried to process this new information. Some continued pursuing the pirates, others moved to secure bank executives, and still others simply stopped, unsure what to do.

In the confusion, Zara's crew made their escape. They stole a maintenance shuttle, abandoned it two docks later, split into three groups to further confuse pursuit, and finally converged on the \textit{Crimson Revenge}.

``All hands prepare for emergency departure!'' Zara shouted as she hit the bridge. ``Chen, fire up the engines. Jax, tell the dock crew we're leaving with or without clearance.''

The \textit{Crimson Revenge} pulled away from Titan Station like a bat out of hell, station security still too disorganized to mount an effective pursuit. It wasn't until they were well clear and preparing for their jump to hyperspace that Zara allowed herself to relax.

``Status report,'' she called out.

``No casualties, minor injuries only,'' Malik reported. ``We didn't get the fake money, but...''

``But we got something better,'' Zara finished, pulling up the account data she'd downloaded. ``Forty-seven million credits, transferred from the bank's hidden slush funds to our accounts. Plus whatever intelligence value Diana Marsh's people will pay for the evidence of the insurance scam.''

``What about Hoffman?'' Jax asked.

``We left him tied up in the maintenance shuttle. Station security will find him soon enough.'' Zara leaned back in her captain's chair. ``He wanted to frame pirates for his crimes. Now he can explain to the authorities how actual pirates exposed his scheme and robbed him blind in the process.''

``Think they'll come after us?''

``The station authorities? Probably. But they'll have their hands full sorting out the mess at the bank. Every executive with dirty hands will be running for cover. By the time they get around to us, we'll be ghosts in the black.''

As the \textit{Crimson Revenge} jumped to hyperspace, leaving the chaos of Titan Station behind, Zara reflected on the operation. It hadn't gone according to plan---they rarely did---but they'd adapted, survived, and come out ahead. More importantly, they'd exposed a corruption that would have devastated thousands of innocent colonists.

``Captain,'' Kira said quietly. ``What we did back there... exposing the bank fraud. That was the right thing to do.''

``Don't get used to it,'' Zara replied, but she was smiling. ``We're pirates, not heroes. It just happened that doing the right thing aligned with robbing those bastards blind.''

But as she looked around at her crew, she saw something in their faces that hadn't been there before. Pride, not just in a successful score, but in having made a difference. They'd stopped powerful people from hurting the powerless, and gotten rich in the process.

Maybe, Zara thought, there was room in the black for a different kind of pirate. One who took from the corrupt and gave... well, gave to themselves, mostly. But sometimes, when the stars aligned just right, they might accidentally do some good along the way.

The thought should have troubled her. Morrison had trained her to be ruthless, to care only for survival and profit. But Morrison was dead, and Zara was writing her own rules now.

``Set course for the belt,'' she ordered. ``Time to disappear for a while and let things cool down. And somebody send a message to Rodriguez. Tell her the banking sector might be experiencing some instability. Could be opportunities for those paying attention.''

As her crew bent to their tasks, Zara allowed herself a moment of satisfaction. They'd pulled off an impossible heist, exposed massive corruption, and lived to tell the tale. Not bad for a girl from the Titan orphanages who was supposed to die young and forgotten.

In the depths of space, word would spread. The Bloodhawk had struck again, but this time the story would be different. This time, the pirates were almost the good guys.

Almost.